Analysis on car sale data

### 2021-01-15 paper.Rmd
Add files via upload

---
title: "Analysis on car sale data"
output: html_document
runtime: shiny
---

@@

In this project we focuses on the carsale dataset that includes data for different car models. Our aim is to determine what customers value the most when buying cars and how is the price influenced by car's properties. Then consumer advice will be given based on the observations for people who want to sell their cars to help them make the most out of their cars.

## Data Tidy

@@

ggarrange(a, b, c, d, ncol = 2, nrow = 2)
ggarrange(e, f, g, h, ncol = 2, nrow = 2)
ggarrange(i, j, ncol = 2, nrow = 2)

```

@@

ggarrange(a, b, c, d, ncol = 2, nrow = 2)
ggarrange(e, f, g, h, ncol = 2, nrow = 2)
ggarrange(i, j, ncol = 2, nrow = 2)

```
The graphs above show the relationship between different factors of the cars and the number of sales of the cars.We can see that most of the factors do not show a strong correlation with the car sales except for three factors related to car size: Length, Wheelbase, and Width. With these three factors, we can see that the samples with highest factors will greatly increase car sales while the rest samples doesn't change car sales much. For the rest of the factors, we see that some of them, such as Engine Size, Horse power. and Fuel Capacity, the sales decrease for some extreme samples, both in the left tail and the right tail.

>>>>

---
title: "Analysis on car sale data"
output: pdf_document
---

@@

## Introduction

In this project we focuses on the carsale dataset that includes data for different car models. Our aim is to determine what customers value the most when buying cars and how are the original price and the second-hand price influenced by car's properties. Then consumer advice will be given based on the observations for people who want to sell their cars to help them make the most out of their cars.

## Data Collection & Data Cleaning

The dataset used in this project will be the Car_sales.csv dataset from Kaggle user GaganBhatia (https://www.kaggle.com/gagandeep16/car-sales). The author collected this dataset from Analytixlabs, and the data now contains the car brand, manufacturer, horsepower, wheelbase, total sales, second-hand value after 10 years, and other specific car details.

@@

ggarrange(a,b,c,d,e,f,g,h,i,j)
```

@@

ggarrange(a,b,c,d,e,f,g,h,i,j)
```
The graphs above show the relationship between different factors of the cars and the number of sales of the cars.We can see that most of the factors do not show a strong correlation with the car sales except for three factors related to car size: Length, Wheelbase, and Width. With these three factors, we can see that the samples with highest factors will greatly increase car sales while the rest samples doesn't change car sales much. For the rest of the factors, we see that some of them, such as Engine Size, Horse power. and Fuel Capacity, the sales decrease for some extreme samples, both in the left tail and the right tail.
